Intrinsic Verification of Parsers and Formal Grammar Theory in Dependent Lambek Calculus

### 2025-03-22 paper/paper.tex
move frisch/cardelli

%% \subsubsection{Typed Grammars}
Frisch and Cardelli introduced the use of a simple type system to reason about
regular expressions up to weak equivalence \cite{frischCardelli}. \steven{They
  use their system in the design of a linear-time algorithm for greedy regular
  expression matching. It is yet unclear if greediness can be encoded in
  \theoryname; however, it appears that our approach in determinizing an NFA is
  quite similar to their algorithm. The biggest difference being that our
  approach uses a global disambiguation strategy while theirs is a local, greedy strategy.
}
Henglein and Nielsen build on this type-theoretic view of grammars, pointing out that the values of the types correspond precisely to the parse trees \cite{henglein_regular_2011}.
Our design of \theoryabbv extends this view of grammars as types to a much broader class of grammars, as well as providing a syntax and equational theory for \emph{parse transformers}, showing that the terms can be viewed not just as parse trees, but as intrinsically verified parsers.

@@

>>>>

%% \subsubsection{Typed Grammars}
Frisch and Cardelli introduced the use of a simple type system to reason about
regular expressions up to weak equivalence \cite{frischCardelli}.
Henglein and Nielsen build on this type-theoretic view of grammars, pointing out that the values of the types correspond precisely to the parse trees \cite{henglein_regular_2011}.
Our design of \theoryabbv extends this view of grammars as types to a much broader class of grammars, as well as providing a syntax and equational theory for \emph{parse transformers}, showing that the terms can be viewed not just as parse trees, but as intrinsically verified parsers.

@@

\steven{
  Is any of this detail useful here, or nah?

  They
  use their system in the design of a linear-time algorithm for greedy regular
  expression matching. It is yet unclear if greediness can be encoded in
  \theoryname; however, it appears that our approach in determinizing an NFA is
  quite similar to their algorithm. The biggest difference being that our
  approach uses a global disambiguation strategy while theirs is a local, greedy strategy.
}
